Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-09-24 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...

\begin{lemma}Given a $d$-dimensional Hilbert space with the set
of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
holds.
\begin{itemize}
\item Let $\delta=\min_{x\in\left(0,1\right)}\left\{ \max\iota\left(x\right)-x,x-\min\iota\left(x\right)\right\} $.
In another word, if $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
\item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
\item $\rho$ is a totally mixed.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and $\min_{x\in\left(0,1\right)}\left\{ \max\widehat{\iota}_{n}\left(x\right)-x,x-\min\widehat{\iota}_{n}\left(x\right)\right\} =1/\left(4n\right)$.
Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
\end{example}

>>>>

\begin{lemma}Given a $d$-dimensional Hilbert space with the set
of all projectors\nb$\events$, and an interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$.
For two mixed state\nb$\rho$ and $\rho'$, if the following conditions
holds.
\begin{itemize}
\item If $\left|x-y\right|\le\delta$, we must have $y\in\iota\left(x\right)$.
\item $\left\Vert \rho-\rho'\right\Vert \le\delta/d$.
\item $\rho$ is a totally mixed.
\end{itemize}
Then, $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.\end{lemma}

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$, and If $\left|x-y\right|\le\left(4n\right)^{-1}$, we must
have $y\in\widehat{\iota}_{n}\left(x\right)$. Therefore, for any
totally mixed state\nb$\rho$ on a $d$-dimensional Hilbert space,
we have
\begin{itemize}
\item If $\left\Vert \rho-\rho'\right\Vert \le1/\left(4dn\right)$, then
$\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$.
\item If $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.
\end{itemize}
\end{example}

### 2017-09-24 prop_letter.tex
prop_letter.tex \section{Gleason} Updating...

The first step toward a finite precision Born rule is to find a way
of replacing the computed probability by an interval. This can be
done by carefully picking a set of intervals and a rule to select
the correct interval when intervals are overlapping. For example,
consider the following collection of overlapping intervals: 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As in
Table~\ref{tab:I_n}, to select the correct interval from these overlapping
intervals~$[\ell,r]$, we define the non-overlapping interior part
of a interval, $\textrm{Int}\left([\ell,r]\right)$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$ and their interior.
Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
are non-overlapping. See Table~\ref{tab:I_2} for a concrete example
when $n=2$.}

\begin{tabular}{ccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
Any odd number & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
Any even number\tabularnewline
with $0<k<2n$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$}\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to
illustrate these intervals and their interior parts more clearly.
\begin{table}
\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$ and their interior.
Although intervals~$[\ell,r]$ are overlapping, their interior~$\textrm{Int}\left([\ell,r]\right)$
are non-overlapping.}

\begin{tabular}{ccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Then, given a real-valued probability~$x$, we will select an interval~$\iota_{n}\left(x\right)=[\ell,r]$
if $x\in\textrm{Int}\left([\ell,r]\right)$.

@@

\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace which the other one projects
onto.
\end{itemize}
\noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is indeed a QIVPM.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we introduce a few technical notions. We call a state~$\rho$
a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
but any pure state is not totally mixed. We also define a notion of
distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
and the set of all states whose distance with $\rho$ is bounded by
$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$,
we have $\rho_{0}\in B_{\epsilon}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{\epsilon}\left(\rho_{0}\right)$.

After we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
and estimate the states consistent with it by the following theorem.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs~\citep{HOSTunpublished}]In a Hilbert space $\Hilb$
of dimension $3$, given any totally mixed state~$\rho$, 
\begin{equation}
B_{\frac{1}{12n}}\left(\rho\right)\subseteq\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)\subseteq B_{1/n}\left(\rho\right)\,.
\end{equation}
\end{thm}\yutsung{Do we need to summarize the proof?}

\noindent In another word, if a state~$\rho'$ is consistent with
$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$. Reversely,
if the distance between $\rho$ and $\rho'$ is bounded by $\frac{1}{12n}$,
then $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
For example, we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the state very close to
$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.

>>>>

The first step toward a finite precision Born rule is to find a way
of replacing the computed probability by an interval. This can be
done by carefully picking a set of intervals and a rule to select
the correct interval when intervals are overlapping. For example,
consider the following collection of overlapping intervals: 
\begin{equation}
\begin{aligned}\mathscr{I}_{n}= & \set{\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]\cap\left[0,1\right]}{k=0,\ldots,2n}\\
 & \cup\{\imposs,\necess\}
\end{aligned}
\end{equation}
which are overlapping intervals with length~$1/n$ except for the
intervals with length~$\left(2n\right)^{-1}$ at each end. As in
Table~\ref{tab:I_n}, to select the correct interval from these overlapping
intervals~$[\ell,r]$, we define the non-overlapping interior part
of a interval, $\textrm{Int}\left([\ell,r]\right)$.
\begin{table}
\caption{\label{tab:I_n}Intervals in $\mathscr{I}_{n}$, their interior, and
their length, where $2\mid k$ means $k$ is even, and $2\nmid k$
means $k$ is odd. Although intervals~$[\ell,r]$ are overlapping,
their interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.
See Table~\ref{tab:I_2} for a concrete example when $n=2$.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{2n}\right]$ & $\left(0,\tfrac{0.5}{2n}\right]$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\nmid k$\tabularnewline
\end{tabular} & $\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$ & $\left(\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right)$ & $\tfrac{1}{n}$\tabularnewline\addlinespace
\midrule 
\addlinespace
\begin{tabular}{c}
$0<k<2n$\tabularnewline
and $2\mid k$\tabularnewline
\end{tabular} & \multirow{1}{*}{$\left[\tfrac{k-1}{2n},\tfrac{k+1}{2n}\right]$} & \multirow{1}{*}{$\left[\tfrac{k-0.5}{2n},\tfrac{k+0.5}{2n}\right]$} & $\tfrac{1}{n}$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2n$ & $\left[\tfrac{2n-1}{2n},1\right]$ & $\left[\tfrac{2n-0.5}{2n},1\right)$ & $\tfrac{1}{2n}$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Table~\ref{tab:I_2} lists a special case $\mathscr{I}_{2}$ to
illustrate these intervals and their interior parts more clearly.
\begin{table}
\caption{\label{tab:I_2}Intervals in $\mathscr{I}_{2}$, their interior, and
their length. Although intervals~$[\ell,r]$ are overlapping, their
interior~$\textrm{Int}\left([\ell,r]\right)$ are non-overlapping.}

\begin{tabular}{cccc}
\toprule 
\addlinespace
$k$ & $[\ell,r]$ & $\textrm{Int}\left([\ell,r]\right)$ & $r-\ell$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
 & $\imposs$ & $\imposs$ & $0$\tabularnewline\addlinespace
\midrule 
\addlinespace
$0$ & $\left[0,\tfrac{1}{4}\right]$ & $\left(0,\tfrac{1}{8}\right]$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
\midrule 
\addlinespace
$1$ & $\left[0,{\textstyle \tfrac{1}{2}}\right]$ & $\left(\tfrac{1}{8},\tfrac{3}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
\midrule 
\addlinespace
$2$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$ & $\left[\tfrac{3}{8},\tfrac{5}{8}\right]$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
\midrule 
\addlinespace
$3$ & $\left[\tfrac{1}{2},1\right]$ & $\left(\tfrac{5}{8},\tfrac{7}{8}\right)$ & $\tfrac{1}{2}$\tabularnewline\addlinespace
\midrule 
\addlinespace
$4$ & $\left[\tfrac{1}{4},1\right]$ & $\left[\tfrac{7}{8},1\right)$ & $\tfrac{1}{4}$\tabularnewline\addlinespace
\midrule 
\addlinespace
 & $\necess$ & $\necess$ & $0$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
 Then, given a real-valued probability~$x$, we will select an interval~$\iota_{n}\left(x\right)=[\ell,r]$
if $x\in\textrm{Int}\left([\ell,r]\right)$.

@@

\noindent Since $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$ clearly satisfies
Eqs.~(\ref{eq:QIVPM-constraints}), the condition really need to
be checked is Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}).
Given $x_{0}$, $x_{1}$, and $x_{0}+x_{1}\in\left[0,1\right]$, it
is easy to verify that
\begin{equation}
\iota_{n}\left(x_{0}+x_{1}\right)\subseteq\iota_{n}\left(x_{0}\right)+\iota_{n}\left(x_{1}\right)\,.\label{eq:iota-add}
\end{equation}
This implies Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
when $P_{0}$ and $P_{1}$ are orthogonal. When $P_{0}$ and $P_{1}$
are not orthogonal on a three-dimensional Hilbert space, we have two
possibilities:
\begin{itemize}
\item Their complements are orthogonal so that we can apply Eq.~(\ref{eq:iota-add})
on their complements.
\item One of them projects onto a subspace of what the other one projects
onto.
\end{itemize}
\noindent No matter which case, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion})
can be deduced easily~\citep{HOSTunpublished}. Therefore, $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
is indeed a QIVPM.

@@

Our framework allows us to generalize the above theorem to Born QIVPMs~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$:
The collection of states consistent $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
gets closer and closer to $\rho$ as the intervals get narrower and
narrower, eventually collapsing to $\rho$ when the intervals become
infinitely precise real numbers covering the real line. To state this
result, we introduce a few technical notions. We call a state~$\rho$
a \emph{totally mixed state} if $0<\mu_{\rho}^{\mathrm{B}}\left(P\right)<1$
for any $P\in\events\backslash\left\{ \mathbb{0},\mathbb{1}\right\} $.
For example, $\rho_{0}$ and $\rho_{1}$ are both totally mixed states,
but any pure state is not totally mixed. We also define a notion of
distance between two states~$\rho$ and $\rho'$ as $\left\Vert \rho-\rho'\right\Vert =\max_{\ip{\psi}{\psi}=1}\left|\melem{\psi}{\rho-\rho'}{\psi}\right|$~\citep{544199},
and the set of all states whose distance with $\rho$ is bounded by
$\epsilon$ is denoted by $B_{\epsilon}\left(\rho\right)=\set{\rho'}{\left\Vert \rho-\rho'\right\Vert \le\epsilon}$.
For example, since $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{24}$~\citep{HOSTunpublished},
we have $\rho_{0}\in B_{1/24}\left(\rho_{1}\right)$ and $\rho_{1}\in B_{1/24}\left(\rho_{0}\right)$.

Since we have enough definitions, we can replace the QIVPM~$\bar{\mu}$
in Thm.~\ref{cor:Gleason's} by a Born QIVPM~$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$,
and estimate the states consistent with it by the following theorem.

\begin{thm}[Finite-precision Extension of Gleason's theorem for the
Born QIVPMs]In a Hilbert space $\Hilb$ of dimension $3$, given
any totally mixed state~$\rho$, 
\begin{equation}
B_{\frac{1}{12n}}\left(\rho\right)\subseteq\coreBorn\left(\iota_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)\subseteq B_{1/n}\left(\rho\right)\,.
\end{equation}
\end{thm}

\noindent In another word, if a state~$\rho'$ is consistent with
$\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$, its distance with $\rho$,
$\left\Vert \rho-\rho'\right\Vert $, must be bounded by $1/n$ which
is the maximal length of the intervals in $\mathscr{I}_{n}$~\citep{HOSTunpublished}.
Conversely, if the distance between $\rho$ and $\rho'$ is bounded
by $\frac{1}{12n}$, their Born quantum probability on any projector~$P$
is $\left|\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)-\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right|\le\frac{1}{4n}$~\citep{HOSTunpublished}.
Moreover, the interiors of the intervals in $\mathscr{I}_{n}$ shrinks
$\frac{0.5}{2n}$ from the both ends, excepts $\imposs$, $\left[0,\tfrac{1}{2n}\right]$,
$\left[\tfrac{2n-1}{2n},1\right]$, and $\necess$. Together with
the fact that $0<\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)<1$ and
$0<\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)<1$, $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$
and $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ are both in the same
intervals, and $\rho'$ is consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$.
For example, we should have $\rho_{1}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$
and $\rho_{0}\in\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}},\events\right)$,
and this is indeed the case for $P\in\events_{C}$ according to Table~\ref{tab:Compute-the-QIVPM}.
In general, as $n$ goes to infinity, only the state very close to
$\rho$ are guaranteed to belong to $\coreBorn\left(\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}},\events\right)$,
and the states consistent with $\iota_{n}\circ\mu_{\rho}^{\mathrm{B}}$
will become closer and closer to $\rho$.
